Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-25 latex/afm-cs-main.tex
Add todos, comment stuff out.

In this work, we use three reconstruction algorithms to generate the final
surface image. The first one comes from the field of compressive sensing (CS).
CS is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, of the fact that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the following observation equation,
\begin{equation}\label{op:observation}
  y = R x = RU\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
$m\times n$ matrix defining the measurements, $U$ is an $n\times n$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
general, $m\ll n$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix.

The symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
They are reused here as they are standard notation in the CS literature; their
specific meaning throughout the paper should be clear from context.

In the AFM application, the probe can only measure a single pixel at a time.
This implies that $R$ is a sparse matrix with each row having only one
nonzero entry and that $y$ is a subset of $x$. Ideally, the sparsity basis and
the measurement matrix $U$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}. In practice,
the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
mutual coherence between the basis and the required structure of the AFM sensing
matrices and providing a high sparsity of typical AFM sample images. In the following,
we assume that $U^TU=I$, though in the simulation and experimental results, we take
$U$ as the DCT basis.

One common realization of the CS-based reconstruction problem, known as basis
pursuit with denoising (BPDN), is given by the following optimization problem,
\begin{equation}
  \min_{x} \left \| U^Tx \right \|_1 \quad
  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
\end{equation}
  where $\| \cdot \|_1$ and $\| \cdot \|_2$ denote $l_1$ and $l_2$ norms,
respectively, and $\sigma$ represents some measure of the signal noise such as
its variance. This problem essentially searches for the sparsest signal from all
the candidates that match the measurements. While BPDN is a computationally
demanding algorithm, particularly for large images, it in general provides
accurate reconstructions.

@@

\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} |U^Tx|_1 + \alpha_v|D_vx|_1 + \alpha_h|D_hx|_1  \label{op:bp_tv}
  % \text{subject to} &\, \| R x - y \|_2 < \sigma,
\end{align}
where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
discrete gradient in the vertical (resp., horizontal) direction and
\begin{align*}
  (\nabla_v X)_{i,j} = 
  \begin{cases}
    X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
    0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
  \end{cases}\\
  (\nabla_h X)_{i,j} = 
  \begin{cases}
    X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
    0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
  \end{cases}
\end{align*}
In \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction. The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
and inpainting (described below), in which the first term seeks a sparse solution while the
last two terms try to diffuse pixel information.
To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
\end{equation*}
where 
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
\end{equation*}
One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
\begin{equation}
  f_{\mu} = \max_{u\in Q_d} \left\langle u,
    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
\end{equation}
The gradient of \eqref{eqn:fcn_prox} is given by
\begin{equation*}
  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
\end{equation*}
where
\begin{equation*}
  (u_{\mu}(x))[i] = 
\begin{cases}
    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
    \text{sgn}(W x[i]), & \text{else}.
  \end{cases}
\end{equation*}

@@

\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[htbp]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV} & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\	
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}	\\
    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}		
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\endgroup

@@

% =========================================================================
\section{Experimental setup} \label{sec:experimentalSetup}
% =========================================================================
Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup_anderssonLab},
consists of an Agilent 5500 AFM, a cRIO-9082 embedded controller (National
Instruments), and a standard desktop computer. Through a breakout box, the
Agilent 5500 provides access to the $x$, $y$, and $z$-axis measurements as well
as the deflection signal (denoted in the following as $l$). When the Agilent
default software (PicoView) is set to open-loop mode, a $\pm 10$ V input on the
control box allows control of the $x$, $y$, and $z$-axis piezos. The N9524A
piezoelectric scanner in the Agilent 5500 provides a maximum scan area of
$90~\mu$m $\times$ 90~$\mu$m in the $xy$ (horizontal) direction and a range of
$20~\mu$m in the $z$ (vertical) direction. Initial engagement of the tip to the
sample is performed using the PicoView software before control is handed over to
the custom controllers.

TKTKT add stuff about nPoint stage and C300.

@@

\begin{enumerate}
\item \textbf{Initialization:} In this state, the user uses the PicoView
  software to bring the tip to the sample with the stepper motor. Once the tip
  is engaged in the surface, the user switches the control from PicoView to the
  custom software in LabView. The system writes parameters including the
  locations of $\mu$-paths from a desktop file to a host-to-FPGA FIFO (first in,
  first out) buffer. Next, the closed-loop control of all the axes through the
  FPGA is enabled and the system performs the following operations.
  \begin{itemize}
  \item \textbf{Read} the starting location of the first $\mu$-path from the
    host-to-FPGA FIFO.
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\item \textbf{$xy$-axis move:} The system moves the tip to the next target
  location.
  \begin{itemize}
  \item \textbf{Set} $x_{ref}$ and $y_{ref}$ to the beginning of the $\mu$-path.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach a settling
    criterion, then go to state 3.
  \end{itemize}
\item \textbf{Tip engage:} The system drives the tip towards the sample surface.
  Here, we use a smaller $K_I$ for the $z$-piezo, which results in a slow
  descent and less windup while the tip is out of contact.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to deflection control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then
    transition to state 4. \todo{Update this}
  \end{itemize}
\item \textbf{Scan:} In this state, the system moves the tip following the
  trajectory of the current $\mu$-path.
  \begin{itemize}
  \item \textbf{Update} $x_{ref}$, and $y_{ref}$ iteratively to follow the
    trajectory of the current $\mu$-path to the end. At the same time, write the
    $x,y,z,$ and deflection measurements to an FPGA-to-host FIFO.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach the end of the
    $\mu$-path,
    % a settling criterion,
    then go to state 5.
  \end{itemize}
  % \item \textbf{Transition decision:} The tip is at the end of the $\mu$-path
  %   at this time. The location of the next $\mu$-path is read from the FIFO.
  %   In
  %   order to accelerate the scanning process, the decision to lift the tip or
  %   not is made in this state. The time $t_{xy\_scan}$ it takes to scan to the
  %   beginning of the next $\mu$-path is compared to
  %   $t_{\textit{z}up}+t_{xy}+t_{\textit{z}down}$. If the former is larger,
  %   then
  %   go to state 6; otherwise, go to state 2.
\item \textbf{Tip withdraw:} In this state, the system withdraws the tip in the
  $z$-direction. A large $K_I$ is used for the $z$-piezo here in order to save
  time.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Set} the $z$ setpoint at a specified distance off the surface.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\end{enumerate}

@@

% \begin{figure}[htbp!]
%   \centering
%     %   \includegraphics[width=3.0in]{figures-SBA/mupathsignaltrajectory}
%   \includegraphics[width=3.0in]{figures-SBA/mupathsignaltrajectory-swapped}
%   \caption{Two cycles of the $\mu$-path scanning process. The top two plots
%   are the lateral motion of the stage, the third is the $z$-sensor signal, and
%   the bottom is the deflection signal. Each stage of the state machine is
%   indicated by color.}
%   \label{fig:mupathsignaltrajectory}
% \end{figure}

% The first section discusses several modifications (i.e., differences to
% Chapter~\ref{chap:cs_init}) to the CS-scanning cycle. Section
% \ref{sec:post_process} discusses the post-processing techniques used. Section
% \ref{sec:rdi} develops a new metric to compare the relative damage done by
% different scans and Section~\ref{sec:psnr_ssim_limits} takes a closer look at
% the SSIM and PSNR metrics in an effort to understand what ''reasonable''
% numbers look like for AFM images taken with our AFM. Similarly,
% Section~\ref{sec:cs_sim} looks at some CS simulations (based on real raster
% scans) to help us understand what, ideally, we should see from the experiments
% performed in Section~\ref{sec:results:final}.

% Several cycles of the CS-scheme are shown in
% Fig.~\ref{fig:mupathsignaltrajectory}. Each of these differences is discussed
% more fully in the following three subsections.
\begin{figure*}[ht!]
  \centering \includesvg[scale=0.85]{figures/cs_cycle.svg}
  \caption{Several CS cycles. Each state is indicated by color.}
  \label{fig:mupathsignaltrajectory}
\end{figure*}

% \begin{figure*}
%   \centering
%   \includesvg[width=.9\textwidth]{figures/state-machine-final.svg}
%   \caption{Diagram of the state-machine implemented in the final design.}
%   \label{fig:sm_final}
% \end{figure*}

\subsection{Cantilever does not need to fully disengage.}
In the initial implementation, we insisted that the during tip-retraction
(state-5), the cantilever tip should fully break contact with the surface. Here,
we impose no such requirement. Rather, we change the $Z$-setpoint during
tip-retraction to only pull away far enough that the deflection signal stays low
(i.e., below the scanning setpoint), even while we run across the surface.

@@

\begin{figure}[ht!]
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
    (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
  \label{fig:z_drift}
\end{figure}

@@

% \subsection{Dynamic de-trending}
% Because our AFM is not equipped with a $Z$-axis sensor, it is important to
% remove as much drift as possible from the $u_Z$ control signal, otherwise,
% this slow dynamic will corrupt the final image. This can partly be achieved by
% doing an image after the AFM has been on for a long time, e.g., 20 minutes,
% and especially after taking several slow raster scans. We can also remove some
% of the drift by fitting a curve
% \begin{equation}
%   d_k = \alpha + \beta t_k + \gamma \log\left(\frac{t_k}{0.1}\right)
% \end{equation}
% where $t_k$ is the time at the $k$-th sampling period and $\alpha$, $\beta$,
% and $\gamma$ are the parameters to be fit. This is a combination of a
% time-domain drift model \cite{Jung_open_loop_2000} and a linear fit which
% accounts for sample tilt. This line is fit to the entire set of $u_Z$ control
% data and subtracted.

\subsection{CS-reconstruction}\label{sec:tv_denoise}
Some of the noise in an image reconstructed via BPDN can be reduced by solving a
Total Variation (TV) de-noising optimization problem
\begin{equation}
  \min_{U} ||\nabla_xU||_1 + ||\nabla_yU||_1 + \mu||F - U||_2 \label{eqn:breg1}
\end{equation}
where $F$ is the image produced by the BPDN optimization and $U$ is the
de-noised image. This idea was heavily inspired by Yufan Luo's approach
\cite{luo_mupath_2019}. The difference is that (i) I do this for both $\nabla_x$
and $\nabla_y$, where he only does it for $\nabla_y$ and (ii) that he does it in
a single optimization which combines \eqref{eqn:breg1} with BPDN while I do it
in two separate optimizations. The optimization is solved using the Split
Bregman technique described in \cite{goldstein_splitbregman_2009} and my
implementation is publicly available \cite{L1c}.

@@

\begin{figure*}
  \includesvg[scale=1]{figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in \ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

>>>>

In this work, we use three reconstruction algorithms to generate the final
surface image. The first one comes from the field of compressive sensing (CS).
CS is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, of the fact that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the following observation equation,
\begin{equation}\label{op:observation}
  y = R x = RU\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^n$ is the observation vector, $R$ is an
$n\times m$ matrix defining the measurements, $U$ is an $m\times m$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
general, $n\ll m$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix.

In the AFM application, the probe can only measure a single pixel at a time.
Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
Ideally, the sparsity basis and
the measurement matrix $R$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}. In practice,
the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
mutual coherence between the basis and the required structure of the AFM sensing
matrices and providing a high sparsity of typical AFM sample images. In the following,
we assume that $U^TU=I$, though in the simulation and experimental results, we take
$U$ as the DCT basis.

Basis pursuit with denoising (BPDN) is one common realization of the CS-based
reconstruction problem, and is given by the optimization
\begin{equation}
  \min_{x} \left \| U^Tx \right \|_1 \quad
  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
\end{equation}
where $\sigma$ represents uncertainty in the measurements. BPDN
essentially searches for the sparsest signal from all
the candidates that match the measurements.

@@

\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} |U^Tx|_1 + \alpha_v|D_vx|_1 + \alpha_h|D_hx|_1  \label{op:bp_tv}
  % \text{subject to} &\, \| R x - y \|_2 < \sigma,
\end{align}
where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
discrete gradient in the vertical (resp., horizontal) direction and
\begin{align*}
  (\nabla_v X)_{i,j} = 
  \begin{cases}
    X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
    0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
  \end{cases}\\
  (\nabla_h X)_{i,j} = 
  \begin{cases}
    X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
    0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
  \end{cases}
\end{align*}
\todo{This is way too long}
In \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction. The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
and inpainting (described below), in which the first term seeks a sparse solution while the
last two terms try to diffuse pixel information.
To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
\end{equation*}
where 
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
\end{equation*}
One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
\begin{equation}
  f_{\mu} = \max_{u\in Q_d} \left\langle u,
    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
\end{equation}
The gradient of \eqref{eqn:fcn_prox} is given by
\begin{equation*}
  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
\end{equation*}
where
\begin{equation*}
  (u_{\mu}(x))[i] = 
\begin{cases}
    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
    \text{sgn}(W x[i]), & \text{else}.
  \end{cases}
\end{equation*}

@@

\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[htbp]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV} & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    % \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
    %                                & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
    %                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
    %                                                                              & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
    %                                                                                                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
    %                                                                                                                                                    & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\	
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}	\\
    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}		
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup

@@

% =========================================================================
\section{Experimental setup} \label{sec:experimentalSetup}
% =========================================================================
Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup_anderssonLab},
consists of an Agilent 5400 AFM, a cRIO-9082 embedded controller (National
Instruments), and a standard desktop computer. Through a breakout box, the
Agilent 5500 provides access to the $x$, $y$, and $z$-axis measurements as well
as the deflection signal (denoted in the following as $l$). When the Agilent
default software (PicoView) is set to open-loop mode, a $\pm 10$ V input on the
control box allows control of the $x$, $y$, and $z$-axis piezos. The N9524A
piezoelectric scanner in the Agilent 5400 provides a maximum scan area of
$90~\mu$m $\times$ 90~$\mu$m in the $xy$ (horizontal) direction and a range of
$20~\mu$m in the $z$ (vertical) direction. Initial engagement of the tip to the
sample is performed using the PicoView software before control is handed over to
the custom controllers.

\todo{ add stuff about nPoint stage and C300.}

@@

\begin{enumerate}
\item \textbf{Initialization:} In this state, the user uses the PicoView
  software to bring the tip to the sample with the stepper motor. Once the tip
  is engaged in the surface, the user switches the control from PicoView to the
  custom software in LabView. The system writes parameters including the
  locations of $\mu$-paths from a desktop file to a host-to-FPGA FIFO (first in,
  first out) buffer. Next, the closed-loop control of all the axes through the
  FPGA is enabled and the system performs the following operations.
    \todo{Shorten this. Sean, what was your trick to not indent enumerate?}
  \begin{itemize}
  \item \textbf{Read} the starting location of the first $\mu$-path from the
    host-to-FPGA FIFO.
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\item \textbf{$xy$-axis move:} The system moves the tip to the next target
  location.
  \begin{itemize}
  \item \textbf{Set} $x_{ref}$ and $y_{ref}$ to the beginning of the $\mu$-path.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach a settling
    criterion, then go to state 3.
  \end{itemize}
\item \textbf{Tip engage:} The system drives the tip towards the sample surface.
  Here, we use a smaller $K_I$ for the $z$-piezo, which results in a slow
  descent and less windup while the tip is out of contact.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to deflection control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then
    transition to state 4. \todo{Update this}
  \end{itemize}
\item \textbf{Scan:} In this state, the system moves the tip following the
  trajectory of the current $\mu$-path.
  \begin{itemize}
  \item \textbf{Update} $x_{ref}$, and $y_{ref}$ iteratively to follow the
    trajectory of the current $\mu$-path to the end. At the same time, write the
    $x,y,z,$ and deflection measurements to an FPGA-to-host FIFO.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach the end of the
    $\mu$-path,
    % a settling criterion,
    then go to state 5.
  \end{itemize}
  % \item \textbf{Transition decision:} The tip is at the end of the $\mu$-path
  %   at this time. The location of the next $\mu$-path is read from the FIFO.
  %   In
  %   order to accelerate the scanning process, the decision to lift the tip or
  %   not is made in this state. The time $t_{xy\_scan}$ it takes to scan to the
  %   beginning of the next $\mu$-path is compared to
  %   $t_{\textit{z}up}+t_{xy}+t_{\textit{z}down}$. If the former is larger,
  %   then
  %   go to state 6; otherwise, go to state 2.
\item \textbf{Tip withdraw:} In this state, the system withdraws the tip in the
  $z$-direction. A large $K_I$ is used for the $z$-piezo here in order to save
  time.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Set} the $z$ setpoint at a specified distance off the surface.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\end{enumerate}

@@

% Several cycles of the CS-scheme are shown in
% Fig.~\ref{fig:mupathsignaltrajectory}. Each of these differences is discussed
% more fully in the following three subsections.

\begin{figure*}[ht!]
  \centering \includesvg[scale=0.85]{figures/cs_cycle.svg}
  \caption{Several CS cycles. Each state is indicated by color.}
  \label{fig:mupathsignaltrajectory}
\end{figure*}
\todo{Make fig \ref{fig:mupathsignaltrajectory}  smaller}

\subsection{Cantilever does not need to fully disengage.}
\todo{Dramatically truncate this section}
In the initial implementation, we insisted that the during tip-retraction
(state-5), the cantilever tip should fully break contact with the surface. Here,
we impose no such requirement. Rather, we change the $Z$-setpoint during
tip-retraction to only pull away far enough that the deflection signal stays low
(i.e., below the scanning setpoint), even while we run across the surface.

@@

% \begin{figure}[ht!]
%   \begin{subfigure}{.48\textwidth}
%     \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
%     \caption{ }
%     % \label{fig: }
%   \end{subfigure}
%   \begin{subfigure}{.48\textwidth}
%     \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
%     \caption{ }
%     % \label{fig: }
%   \end{subfigure}
%   \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
%     (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
%   \label{fig:z_drift}
% \end{figure}

@@

@@

\begin{figure*}
  \includesvg[scale=1]{figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}
